### 2019-01-28 thesis_report/introduction.tex
Updated thesis
updated thesis
Semi-acceptable version of methods and resutls

\chapter{Introduction}

\comment{We propose that the introduction of a zigzag-shaped modulation of the junction region leads to an increased topological gap, as well as a reduction of the Majorana coherence length.}
\comment{We hypothesize that the gap improvement is the result of the elimination of long trajectories}

>>>>

% -*- root: ./report.tex -*-
\chapter{Introduction}
% \comment{We propose that the introduction of a zigzag-shaped modulation of the junction region leads to an increased topological gap, as well as a reduction of the Majorana coherence length.}
% \comment{We hypothesize that the gap improvement is the result of the elimination of long trajectories}

Majorana bound states (MBSs) are a promising candidate to form the basis of a stable platform for topological quantum computing.

\comment{Majoranas are mostly made in hybrid NS structures.}
The current experimental effort is focused on creating pairs of MBSs in hybrid normal-superconductor (NS) structures, where a lengthy strip (or wire) of semiconductor is interfaced with a \cite{lutchyn_majorana_2010,oreg_helical_2010} superconductor.
Within the right parameter regime ($E_z^2>\mu^2+\Delta^2$ for a simple wire), the semiconductor becomes topological and MBSs appear at the ends of the segment.
Recently, a system with a slight modification has been proposed\cite{pientka2017topological}, where instead of having one superconductor, there are two superconductors, creating a superconductors-normal-superconductor (SNS) junction.
This adds an extra knob to adjust, the superconducting phase difference $\phi$, and this should make it easier to tune the system into the topological phase.
In practice, multiple problems arise making even the observation, let alone the manipulation of Majoranas difficult.

\comment{The gap is small because of long trajectories.}
One of the biggest challenges in creating stable Majoranas is the appearance of a soft gap; where the gap in the density of states is greatly reduced for states with the momentum directed along the length of the strip.
From a semiclassical perspective, these momenta correspond to long paths through the semiconductor without interruption by the superconductor.
Additionally, these long trajectories have long flight times $\tau_f$ and equivalenly small Thouless energies $E_{\textrm{Th}}=\hbar / \tau_f$, resulting in a small gap.

\comment{Currently proposed workarounds are low density or disorder, but both have drawbacks.}
Currently, proposed workarounds are low density or disorder~\cite{haim_double-edge_2018}, but both have drawbacks.

\comment{We show that zigzag geometry solves this problem by eliminating the long trajectories.}
In this paper we show that introducing a zigzag or snake like geometry for the semiconductor eliminates these long trajectories and prevents the appearance of a soft gap while also increasing the topological gap by an order of magnitude.

### 2019-01-28 thesis_report/methods.tex
Added to bandstructures and wavefunctions.
New parts added to results
Semi-acceptable version of methods and resutls

@@

	\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.95\columnwidth]{figures/kwant_system}
	\caption{Figure of different examples of simulated systems in Kwant.
	Lattice spacing is made smaller to make the discretization visible.
	The two golden regions are both superconducting, but differ in phase.
	The blue and black regions form the semiconductor, but the black region has an optional potential offset to model an imperfect interface, increasing the amount of normal reflection.}
	\label{fig:kwant_system}
	\end{figure}

	\comment{We use kwant to make systems and extract the eigenstates}
	We use a tight-binding model, implemented using Kwant, to simulate various properties of the system.
	The model consists of a two-dimensional square lattice of sites.
	Each site has two orbitals: spin and electron-hole.
	There are four different types of sites (and thus four different Hamiltonians): the top superconductor, the bottom superconductor, the normal region, and a normal region with a variable potential offset, forming a barrier to simulated an imperfect NS interface.
	A schematic of such kwant systems is depicted in Fig.~\ref{fig:kwant_system}.
	After the system is specified, we can extract the total Hamiltonian of the system, allowing analysis of the eigenstates.

	\comment{We extract the gap by either taking the lowest energy state for an infinite system, or the difference between the lowest two eigenstates.}

@@

		We derive the spectrum by calculating the scattering matrix for the normal region and applying the Andreev bound state condition for the short junction limit\cite{beenakker1991universal, sticlet_robustness_2017}. 
		The short junction limit is valid for [TODO: WHEN IS THE SHORT JUNCTION LIMIT VALID]
		For deriviation of the scattering matrix, we neglect SOI in the transverse direction, which is valid for $W<l_\text{so}$.

@@

			To solve the system analytically, we use the Short Junction limit: we set the energy to zero.
			By applying the boundary conditions and solving the resulting linear system of equations, the resulting solution is given by Eqs.~\eqref{eq:smatrix} through ~\eqref{eq:momenta_short_junction}.
			\emph{Important note: In order to use the Andreev bound state condition, the scattering matrix must be in the [TODO: NAME OF BASIS] basis. This basis transformation has already been applied in Eqs. ~\eqref{eq:smatrix} through ~\eqref{eq:momenta_short_junction}}\\

@@

			\begin{equation}
			\det\left[1+\alpha^{2}\left(E\right)r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right)\right]=0
			\end{equation}

>>>>

\section{Physical picture}
	\comment{We consider a two-dimensional system with zigzag.}
	We consider a Josephson junction (JJ)(Fig.~\ref{fig:setup}) consisting of a two dimensional strip of semiconductor, with superconductors on both sides.
	We modulate the shape of the normal region, which can be either zigzag as depicted, or a more smooth sinusoidal like shape.
	Similar to the conventional straight system \cite{pientka2017topological}, a magnetic field $B_x$ perpendicular to the junction is applied.
	We model the system with a BdG Hamiltonian Eq.~\eqref{eq:hamiltonian}; the normal part has a linear Rashba spin-orbit coupling term characterized by $\alpha$ and a Zeeman field with $E_z=\frac{1}{2}mu_B g B_x$.
	The superconductor has a superconducting coupling term $\Delta$ with a superconducting phase $\exp{\pm i \phi/2}$.
	Both parts have a kinetic term and chemical potential $\mu$ (counted from the bottom spin-orbit band). 
	For the zigzag geometry, we first consider a sawtooth like pattern where $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.

	\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.5\columnwidth]{images/zigzag.pdf}
	\caption{Setups. Figure of a straight and zigzag system, including trajectories.
	\label{fig:setup}}
	\end{figure}

	\comment{The symmetry class of the system is D.}
	The non-zigzag system is in the symmetry class BDI \cite{pientka2017topological}.
	Using the software package Qsymm\cite{varjas2018qsymm}, we find that the symmetry class of our system to be $\mathcal{D}$ because we break the chiral/time-reversal resulting from the mirror symmetric junction.

	\begin{small}
	\begin{align}
	    H = \left(\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu + \frac{\meff \alpha^2}{2 \hbar^2} \right)\tau_z+
	        E_\text{z} \sigma_x+
	        \alpha \left( \ky \sigma_x - \kx \sigma_y \right) \tau_z +
	        \Delta \tau_y
	\end{align}
	\label{eq:hamiltonian}
	\end{small}

@@

	\comment{We use kwant to make systems and extract the eigenstates}
	We use a tight-binding model, implemented using Kwant, to simulate various properties of the system.
	The model consists of a two-dimensional square lattice of sites.
	Each site has two orbitals: spin and electron-hole.
	There are four different types of sites (and thus four different Hamiltonians): the top superconductor, the bottom superconductor, the normal region, and a normal region with a variable potential offset, forming a barrier to simulated an imperfect NS interface.
	A schematic of such kwant systems is depicted in Fig.~\ref{fig:kwant_system}.
	We can also make the system infinite in for example the $x$ direction by connecting the sites on the left border with those on the right border with a $\kx$ dependent hopping.

	\begin{figure}[!htb]
	\centering
	\includegraphics[width=0.95\columnwidth]{figures/kwant_system}
	\caption{Figure of different examples of simulated systems in Kwant.
	Lattice spacing is made bigger to make the discretization visible.
	The two golden regions are both superconducting, but differ in phase.
	The blue and black regions form the semiconductor, but the black region has an optional potential offset to model an imperfect interface, increasing the amount of normal reflection.}
	\label{fig:kwant_system}
	\end{figure}

	\comment{We extract the gap by either taking the lowest energy state for an infinite system, or the difference between the lowest two eigenstates.}
	After the system is specified, we can extract the total Hamiltonian of the system, allowing analysis of the eigenstates.
	For example, calculating the bandstructure of a system is performed by taking a translationally invariant system and calculating the eigenvalues for different momenta.

@@

		We derive the spectrum by calculating the scattering matrix for the normal region and applying the Andreev bound state condition for the short junction limit\cite{beenakker1991universal, sticlet_robustness_2017}. 
		The short junction limit is valid for $W<\xi$, where $\xi$ is the superconducting coherence length.
		For deriviation of the scattering matrix, we neglect SOI in the transverse direction, which is valid for $W<l_\text{so}$.

@@

			To solve the system analytically, we use the Short Junction limit: we set the energy to zero.
			By applying the boundary conditions and solving the resulting linear system of equations, the resulting solution is given by Eqs.~\eqref{eq:smatrix} through ~\eqref{eq:momenta_short_junction}.
			\emph{Important note: In order to use the Andreev bound state condition, the scattering matrix must be in the correct basis. The relevant basis transformation has already been applied in Eqs. ~\eqref{eq:smatrix} through ~\eqref{eq:momenta_short_junction}}.\\

@@

			\begin{equation}
			\det\left[1+\alpha^{2}\left(E\right)r^{*}S_{e}\left(E,\bm{k}\right)rS_{e}^{*}\left(-E,-\bm{k}\right)\right]=0
			\label{eq:bound_state_condition_sjl}
			\end{equation}
